\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-21 papers/jss/article.Rnw
Add back a reference to Tierney's serialization doc.
Move my incomplete TODO performance summary subsection to the final
conclusion/summary section, where I will likely delete most of it but
may use a bit of those ideas in wrapping everything up in a
conclusion.  Ditto for the commented out other approaches section.

Section 6 previously ended on a pessimistic note and a sentence
fragment (the table shows protobuf doesn't do much better in
compression size than normal R serialization).

End on a more complete note that mentions that RProtoBuf is most
benefetial when multiple languages are invo

%FIXME Introductory section which may include references in parentheses
%\citep{R}, or cite a reference such as \citet{R} in the text.

@@

The previous sections discussed functionality in the \pkg{RProtoBuf} package
for creating, manipulating, parsing and serializing Protocol Buffer
messages of a pre-defined schema.  This is useful when there are
pre-existing systems with defined schemas or significant software
components written in other languages that need to be accessed from
within R.

@@

\begin{itemize}
\item normal R serialization,
\item R serialization followed by gzip,
\item normal Protocol Buffer serialization, and
\item Protocol Buffer serialization followed by gzip.
\end{itemize}

@@

Table~\ref{tab:compression} shows the sizes of 50 sample R datasets as
returned by object.size() compared to the serialized sizes.
%The summary compression sizes are listed below, and a full table for a
%sample of 50 datasets is included on the next page.  
Sizes are comparable but Protocol Buffers provide simple getters and setters
in multiple languages instead of requiring other programs to parse the R
serialization format.% \citep{serialization}.
One takeaway from this table is that RProtoBuf does not in general provide
any significant saving in file size compared to the normal serialization
mechanism in R which is seen as equally compact.  The benefit from RProtoBuf
comes from its interoperability with other environments, as well as its safe
versioning,

@@

\subsection{Performance considerations}

>>>>

@@

The previous sections discussed functionality in the \pkg{RProtoBuf} package
for creating, manipulating, parsing and serializing Protocol Buffer
messages of a defined schema.  This is useful when there are
pre-existing systems with defined schemas or significant software
components written in other languages that need to be accessed from
within R.

@@

\begin{itemize}
\item normal R serialization \citep{serialization},
\item R serialization followed by gzip,
\item normal Protocol Buffer serialization, and
\item Protocol Buffer serialization followed by gzip.
\end{itemize}

@@

Table~\ref{tab:compression} shows the sizes of 50 sample R datasets as
returned by object.size() compared to the serialized sizes.
%The summary compression sizes are listed below, and a full table for a
%sample of 50 datasets is included on the next page.  
Sizes are comparable but Protocol Buffers provide simple getters and setters
in multiple languages instead of requiring other programs to parse the R
serialization format. % \citep{serialization}.
One takeaway from this table is that the universal R object schema
included in RProtoBuf does not in general provide
any significant saving in file size compared to the normal serialization
mechanism in R.
% redundant: which is seen as equally compact.
The benefits of RProtoBuf accrue more naturally in applications where
multiple programming languages are involved, or when a more concise
application-specific schema has been defined.  The example in the next
section provides both of these conditions.

@@
